Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-09 ATVA 2025/Comparison.tex
update

>>>>

\textcolor{red}{Fig2 page10 is intended as a running example: We show how $s_{FSB}$ behaves on Fig2 (page10-11). Page12 (Fig4 and above), we explain how SAS computes the same case and compares with FSB. We will add explicit references to the case $c<0,d<0$ leading to $s_{FSB}=\frac{cd}{4}$, which corresponds in Figure4 to either case	
	(b) $\Delta(\hat{b})=\Delta(b)<\frac{c}{2}$ leading to $s_{SAS}=d\Delta(b)<\frac{cd}{2}$ or
	(c) $\Delta(\hat{b})=0$ leading to $s_{SAS}=0$.}

### 2025-04-09 ATVA 2025/experiments.tex
update

>>>>

\textcolor{red}{Currently, for hard instances, there is no alternative  to pMILP (hundreds of seconds), other methods being $>>10$ times slower.}

\textcolor{red}{We did run and reported other tools as best as we could (see also appendixC (Table11...)). Reporting *some* experimental numbers from other papers (Figure5) is standard in the DNN verification community (eg [26]).}
